A neural coarse graining theory of consciousness

### 2018-10-26 Paper_neural_coarse_graining_of_consciousness.tex
Updates from ShareLaTeX
Update

	\section{Neural coarse-graining}
		\subsection{intro}
			\begin{ants}
				@ As we mentioned above, to construct the NTIC process can bring agents great survival advantage.

				@ However, to achieve NTIC (or even IC) is challenging for highly stochastic systems. Due to the stochasticity, the current states of the system have low predictability of its future states.

				@ Previous research has been showing that the neural system are suffered from multiple noise sources  during information processing, including sensory, cellular, electrical, synaptic noises and have large trial-to-trial variability at the cellular level. \citep{faisal2008noise}. neurons are noisy: the same pattern of activity never occurs twice, even when the same stimulus is presented.

				@ \rewrite{Neurons are subject to thermal fluctuations and other physical noise (Faisal et al., 2008).} \cite{faisal2008noise}

				@ These noises sabotaged the predictability of future states and prevent the neural system from creating NTIC processes at the cellular level.

				@ And every individual sensor only receives a little amount of information about the environment.

				@ We argues that the human neural system to achieve NTIC through coarse-graining. 
			\end{ants}

@@

				@ Therefore, most of the high level cognitions can utilise the state of informational closure.

>>>>

	\section{Neural coarse-graining}

		Nevertheless, to achieve information closure (so as NTIC) in highly stochastic systems (e.g., the neural system) is challenging. The current states of the system have low predictability of its future states due to the stochasticity. Information processing in the neural system is suffered from multiple noise sources throughout, including sensory, cellular, electrical, and synaptic noises. Previous studies have shown that states of neurons have large trial-to-trial variability at the cellular level. That is, the same pattern of activity never occurs twice even when the same stimulus is presented. Neurons are inevitably subject to thermal fluctuations and other physical noises \citep{faisal2008noise}. Furthermore, environmental information is always only partial observable to individual sensors and neurons which only receive little amount of information from the environment. Therefore, self and environmental predictive information is difficult to be represented at the cellular level. It is implausible to construct NTIC processes at this level.

		However, to overcome the difficulty, the neural system to achieve NTIC through coarse-graining.

@@

				@ Therefore, most of the high level cognition can utilise the state of informational closure.
